\chapter{Analysis}
\section{Current state-of-the-art and role-models}
Competitors and systems akin to ours.

\section{Common Usage Scenario}
\subsection{Common usage scenarios}
\textit{incl. context}
The most common usage scenario would include medical staff interfacing with the system. The staff would log into the system with their RFID tag. The next course of action would be to perform a measurement. The staff presses the button "Udfør Måling" to do a measurement. This prompts the staff to scan the barcode on the  device which is used to perform the measurement. After the measurement is done the user is prompted to approve or discard the measurement. If the user chooses approve, the measurement results page is shown. If the user chooses discard, the do measurement page is shown.\\
Other common usage scenarios include: Looking at patient information, patient history or doctors comments.

\subsection{Related use cases}

\begin{table}[H]
    \begin{tabular}{|p{4cm}|p{8cm}|}
    \hline
    Name          & Do Measurement "Udfør Måling"   \\\hline
    Actors        & Doctor \\\hline
    Main Scenario & (1) Log Onto System with RFID tag. \\
    ~             & (2) Press "Udfør Måling". \\
    ~             & (3) Scan barcode on wanted device. \\
    ~             & (4a) Approve result \\         
    ~             & (5a) Measurements results are shown.\\\hline
    
    Alternate Scenario & (4b) Discard result \\
        ~             & (5b) go to (3).\\\hline
    \end{tabular}
\end{table}



\section{User Groups and stakeholders}
\subsection{Primary user group}
Henning

\subsection{Primary stakeholders}
Flemming

\subsection{Secondary user group}
asdf

\subsection{Secondary stakeholders}
dsfg
